TO ADD

We should specify the role of irradiation in calculation. At least on Estimator 2 and 3. Because the irradiation model output depends on the FLM in output. 
So Find a way to present this
And Think about a fixed output 



Since the 1990s, many different nuclear fuel cycle simulators have been developed by several institutions.

A fuel cycle simulator aims to model an entire fleet of nuclear facilities such as nuclear reactors, fuel fabrication plants, reprocessing plants, cooling pools, and waste repositories.
These tools help to identify drivers and interactions between parameters in the fuel cycle.
They implement physics models for key points in the cycle such as fuel enrichment, fabrication, and depletion, with various levels of complexity.

Fuel cycle simulators are used worldwide for wide range of applications: optimizing industrial operation of an existing nuclear fleet, assessing the future of nuclear energy, providing valuable information to political decision-makers, and evaluating/verifying the operation of an existing nuclear fleet by national or international safety authorities.
Moreover, these tools are used for Research and Development training as access point to key data related to the fuel cycle.

The myriad institutions that develop and use fuel cycle simulators pursue myriad goals.
Consequently, software development decisions (e.g. fidelity) are often made in accordance with the institution's simulation goals. To improve confidence in the results, institutions may be tempted to increase the complexity of their software even if this complexity might not be necessary.

As an example, neutron and gamma dose calculations require the precise knowledge of each material isotopic composition in each facility as well as a description of the spatial configuration of these isotopes whereas uranium consumption calculation does not require the same degree of detail.
As a consequence, some functionalities may not be needed depending on the technical question the code assesses: solving a given technical question associated with a targeted precision will require a limited set of functionality.
Knowing the importance of each will help users choose an appropriate software tool or may guide future code development to solve a specific question.
Also, some technical issues are assessed by numerous studies performed with different software and it is often difficult to compare them.
Knowing the impact of functionalities on different simulation outputs helps to estimate the level of confidence of the different fuel cycle studies.

The \gls{FIT} Project has been conceived to understand the circumstances under which the choice of algorithm and/or model influences the conclusions that one might draw from a fuel cycle simulation.
The project aims to characterize the relationship between model fidelity and desired confidence level in the context of many differing research questions.
Among functionalities of interest, this first \gls{FIT} focuses on the ability of fuel cycle software to adapt the fresh fuel to the qualities of the available material and the associated reactor requirements.

Section \ref{sec:framework} describes the \gls{FIT} project, its philosophy, the participants, and associated simulators.
It explains how the \gls{FIT} project is not a traditional benchmark.
That is, \gls{FIT}does not aim to do inter-simulator comparison, but focuses on intra-simulator comparison, evaluating differences between simulation results produced by the same simulator, enabling and disabling isolated features.
In order to build confidence in the conclusion, such comparison will be performed across multiple simulators.
Section \ref{sec:framework} ends with the description of the particular feature tested in this work, the fuel loading management model.
Section \ref{sec:exercise} then presents the numerical experiment used to test this particular feature, including simulation input parameter descriptions and other technical specifics necessary to perform the test.
Additionally, this section details output metrics that quantify the impact of the use of fuel loading management in fuel cycle studies.
Next, Section \ref{sec:results} is dedicated to the discussion of results achieved by each software tool involved in this first exercise.
Finally, in Section \ref{sec:conclusion} some conclusions are drawn.
